Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-21 talk/pepm2011/paper.tex
add line numbers

\lstset{
  basicstyle=\setstretch{1.1}\ttfamily\footnotesize,
  language=Python,
  keywordstyle=\bfseries,
  stringstyle=\color{blue},
  commentstyle=\color{gray}\textit,
  fancyvrb=true,
  showstringspaces=false,
  %keywords={def,while,if,elif,return,class,get,set,new,guard_class}
  numberstyle = \tiny,
  numbersep = 0pt,
}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt]
$p_{5}$ = new(BoxedInteger)
set($p_{5}$, intval, $i_{4}$)
$p_{6}$ = new(BoxedInteger)
set($p_{6}$, intval, -100)
\end{lstlisting}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt]
guard_class($p_{5}$, BoxedInteger)
# inside BoxedInteger.add
$i_{7}$ = get($p_{5}$, intval)
guard_class($p_{6}$, BoxedInteger)
# inside BoxedInteger.add__int
$i_{8}$ = get($p_{6}$, intval)
$i_{9}$ = int_add($i_{7}$, $i_{8}$)
\end{lstlisting}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt]
$i_{9}$ = int_add($i_{4}$, -100)
\end{lstlisting}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt]
$p_{15}$ = new(BoxedInteger)
set($p_{15}$, intval, $i_{14}$)
$p_{10}$ = new(BoxedInteger)
set($p_{10}$, intval, $i_{9}$)
jump($p_{15}$, $p_{10}$)
\end{lstlisting}

@@

\begin{figure}
\begin{lstlisting}[mathescape,numbers=right,escapechar=|,numberstyle = \tiny,numbersep=0pt, numberblanklines=false]
# arguments to the trace: $p_{0}$, $p_{1}$ |\setcounter{lstnumber}{2}|
guard_class($p_1$, BoxedInteger)           |\setcounter{lstnumber}{4}|
$i_2$ = get($p_1$, intval)
guard_class($p_0$, BoxedInteger)           |\setcounter{lstnumber}{7}|
$i_3$ = get($p_0$, intval)
$i_4$ = int_add($i_2$, $i_3$)              |\setcounter{lstnumber}{25}|
$i_9$ = int_add($i_4$, -100)               |\setcounter{lstnumber}{35}|

>>>>

\lstset{
  basicstyle=\setstretch{1.1}\ttfamily\footnotesize,
  language=Python,
  keywordstyle=\bfseries,
  stringstyle=\color{blue},
  commentstyle=\color{gray}\textit,
  fancyvrb=true,
  showstringspaces=false,
  %keywords={def,while,if,elif,return,class,get,set,new,guard_class}
  numberstyle = \tiny,
  numbersep = -20pt,
}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt,numbers=right,escapechar=|, firstnumber=10]
$p_{5}$ = new(BoxedInteger)   |\setcounter{lstnumber}{11}|
set($p_{5}$, intval, $i_{4}$) |\setcounter{lstnumber}{14}|
$p_{6}$ = new(BoxedInteger)   |\setcounter{lstnumber}{16}|
set($p_{6}$, intval, -100)
\end{lstlisting}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt,numbers=right,escapechar=|, firstnumber=20]
guard_class($p_{5}$, BoxedInteger)  |\setcounter{lstnumber}{21}|
$i_{7}$ = get($p_{5}$, intval)
guard_class($p_{6}$, BoxedInteger)  |\setcounter{lstnumber}{24}|
$i_{8}$ = get($p_{6}$, intval)
$i_{9}$ = int_add($i_{7}$, $i_{8}$)
\end{lstlisting}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt,numbers=right,escapechar=|, firstnumber=26]
$i_{9}$ = int_add($i_{4}$, -100)
\end{lstlisting}

@@

\begin{lstlisting}[mathescape,xleftmargin=20pt,numbers=right,escapechar=|, firstnumber=44]
$p_{15}$ = new(BoxedInteger)               |\setcounter{lstnumber}{45}|
set($p_{15}$, intval, $i_{14}$)            |\setcounter{lstnumber}{26}|
$p_{10}$ = new(BoxedInteger)               |\setcounter{lstnumber}{28}|
set($p_{10}$, intval, $i_9$)               |\setcounter{lstnumber}{54}|
jump($p_{15}$, $p_{10}$)
\end{lstlisting}

@@

\begin{figure}
\begin{lstlisting}[mathescape,numbers=right,escapechar=|, numberblanklines=false]
# arguments to the trace: $p_{0}$, $p_{1}$ |\setcounter{lstnumber}{2}|
guard_class($p_1$, BoxedInteger)           |\setcounter{lstnumber}{4}|
$i_2$ = get($p_1$, intval)
guard_class($p_0$, BoxedInteger)           |\setcounter{lstnumber}{7}|
$i_3$ = get($p_0$, intval)
$i_4$ = int_add($i_2$, $i_3$)              |\setcounter{lstnumber}{25}|
$i_9$ = int_add($i_4$, -100)               |\setcounter{lstnumber}{35}|
